Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-05-13 reports/manuscript.Rmd
Add wordcount
Inital refactor of manuscript info

authornote: |
  Add author notes here

abstract: |
  Add abstract here

keywords          : "keywords"
wordcount         : "X"

@@

```{r setup, include=FALSE}
Sys.setenv("RSTUDIO_VERSION" = "1.4.1725")
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE
)

@@

```{r, load-targets}
targets::tar_load(c(
    "prisma", "effects_clean", "reviews_tables", "tables_df",
    "plots", "studies_results", "studies_converted",
    "comparison_plots", "combined_effects", "combined_bib"
),
store = here::here("_targets")
)
```

@@

```{r results}
rename_effects <- function(cur_name) {
    if (str_detect(cur_name, ":")) {
        cur_name_split <- str_split(cur_name, ": ")
        return(str_to_lower(paste(
            cur_name_split[[1]][2],
            cur_name_split[[1]][1]
        )))
    } else {
        return(str_to_lower(cur_name))
    }
}
rename_effects <- Vectorize(rename_effects)

unique_effects <- nrow(effects_clean %>% filter(use_effect))

freq_exposures <- effects_clean %>%
    group_by(plain_language_exposure) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    mutate(
        plain_language_exposure = rename_effects(plain_language_exposure),
        plain_language_exposure = case_when(
            plain_language_exposure ==
                "lifestyle risk behaviour (at school) intervention" ~
            "screen-based lifestyle risk behaviour interventions (at school)",
            plain_language_exposure == "general tv programs and movies" ~
            "general TV programs and movies",
            TRUE ~ plain_language_exposure
        ),
        out = paste0(plain_language_exposure, " (*n* = ", n, ")")
    )

freq_outcomes <- effects_clean %>%
    group_by(plain_language_outcome) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    mutate(
        plain_language_outcome = rename_effects(plain_language_outcome),
        plain_language_outcome = case_when(
            plain_language_outcome == "duration sleep" ~ "sleep duration",
            TRUE ~ plain_language_outcome
        ),
        out = paste0(plain_language_outcome, " (*n* = ", n, ")")
    )

freq_combos <- effects_clean %>%
    group_by(plain_language_exposure, plain_language_outcome) %>%
    summarise(n = n()) %>%
    arrange(desc(n))

effects_sum <- effects_clean %>%
    filter(use_effect) %>%
    group_by(covidence_review_id, moderator_age) %>%
    slice_max(n, with_ties = TRUE) %>%
    ungroup() %>%
    summarise(
        sum_k = sum(k, na.rm = TRUE),
        sum_n = sum(n)
    )
```

The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were duplicates.
After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
Of those, `r prisma$data$value[8]` met the inclusion criteria and we extracted the data from all of these meta-analyses.
Figure \@ref(fig:prisma) presents the full results of the selection process.

@@

The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
Supplementary File 3 provides a list of all exposures identified.
The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination for an age group, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.

@@

```{r quality}
qual_data <-
    tables_df %>%
    filter(table == "main") %>%
    distinct(covidence_id, .keep_all = TRUE) %>%
    select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed)

reviews_count <- qual_data %>%
    mutate(
        across(
            eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
            as.factor
        )
    ) %>%
    rowwise() %>%
    mutate(
        count_low = sum(
            c_across(
                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
            ) == "low"
        ),
        count_high = sum(
            c_across(
                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
            ) == "high"
        ),
        count_high_unclear = sum(
            c_across(
                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
            ) %in% c("high", "unclear")
        )
    )

all_low <- reviews_count %>%
    filter(count_low == 7) %>%
    nrow()

all_high <- reviews_count %>%
    filter(count_high == 7) %>%
    nrow()

all_high_unclear <- reviews_count %>%
    filter(count_high_unclear == 7) %>%
    nrow()

all_high_txt <-
    paste0(
        str_to_sentence(numbers_to_words(all_high)),
        if (all_high > 1 | all_high == 0) " meta-analyses" else " meta-analysis"
    )

all_high_unclear_txt <-
    paste0(
        numbers_to_words(all_high_unclear),
        if (all_high_unclear > 1 | all_high_unclear == 0) {
            " meta-analyses"
        } else {
            " meta-analysis"
        }
    )

reviews_count <-
    reviews_count %>%
    select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>% # nolint
    gather(name, value) %>%
    count(name, value) %>%
    arrange(desc(n))

qual_str <- function(n, totaln, ntype = "", prefix = "(*n*", suffix = ")") {
    paste0(
        prefix, ntype, "= ", n, "/",
        totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix
    )
}

n_low_hetero <-
    reviews_count[reviews_count$name == "heterogeneity_assessed" &
        reviews_count$value == "low", "n"][[1]]
n_low_char <-
    reviews_count[reviews_count$name ==
        "included_studies_listed_with_important_characteristics_and_results_of_each" & # nolint
        reviews_count$value == "low", "n"][[1]]
n_low_search <-
    reviews_count[reviews_count$name ==
        "literature_search_strategy_comprehensive_and_systematic" &
        reviews_count$value == "low", "n"][[1]]

n_unclear_elig <-
    reviews_count[reviews_count$name ==
        "eligibility_criteria_predefined_and_specified" &
        reviews_count$value == "unclear", "n"][[1]]

n_high_dualscreen <-
    reviews_count[reviews_count$name == "dual_independent_screening_review" &
        reviews_count$value == "high", "n"][[1]]
n_unclear_dualscreen <-
    reviews_count[reviews_count$name == "dual_independent_screening_review" &
        reviews_count$value == "unclear", "n"][[1]]

n_high_dualquality <-
    reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
        reviews_count$value == "high", "n"][[1]]
n_unclear_dualquality <-
    reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
        reviews_count$value == "unclear", "n"][[1]]

dualqualstr <- paste0(
    qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix = "; "),
    qual_str(
        n_unclear_dualquality,
        nrow(qual_data), " unclear  ",
        prefix = "n", suffix = ")"
    )
)
```

The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of meta-analyses)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
Most reviews did not clearly report if their eligibility criteria were predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
Many papers also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
A similar trend was observed for dual independent quality assessment `r dualqualstr`.
Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.

@@

Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
Our results represent the findings from `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.

>>>>

abstract: |
  Can i have `r print('words')` here?

keywords          : "keywords"
wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE
)

@@

```{r, load-targets}
targets::tar_load(c(
    "manuscript_info", "combined_bib", "reviews_tables",
    "plots", "studies_results", "studies_converted",
    "comparison_plots", "combined_effects", "combined_bib"
),
store = here::here("_targets")
)
```

@@

The searches yielded `r format(manuscript_info$prisma$search, big.mark=",")` results, of which `r format(manuscript_info$prisma$duplicates, big.mark=",")` were duplicates.
After screening titles and abstracts, we assessed `r format(manuscript_info$prisma$full_text, big.mark=",")` full-texts for inclusion.
Of those, `r manuscript_info$prisma$included` met the inclusion criteria and we extracted the data from all of these meta-analyses.
Figure \@ref(fig:prisma) presents the full results of the selection process.

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 3 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

@@

The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.

@@

Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
